When does vapor pressure deficit drive or reduce evapotranspiration?

### 2017-10-10 doc/paper/vpd_et_paper.tex
starting to work on Pierre's comments

Changes to vapor pressure deficit (VPD) alter the atmospheric demand for water from the land surface. However, plant stomata have evolved to optimally regulate the exchange of water and carbon between vegetation and the atmosphere \citep{Franks_2017}. Therefore, an increase (decrease) in VPD may not correspond to an increase (decrease) in evapotranspiration (ET) because stomatal closure (opening) can cancel the effects of shifts to atmospheric demand.

>>>>

Changes to vapor pressure deficit (VPD) alter the atmospheric demand for water from the land surface. Atmospheric scientists and hydrometeorologists generally think that an increase in atmospheric demand induces an increases in evapotranspiration (ET). However, plant stomata have evolved to optimally regulate the exchange of water and carbon between vegetation and the atmosphere \citep{Franks_2017}. Therefore, an increase (decrease) in VPD may not correspond to an increase (decrease) in ET stomatal closure (opening) can cancel the effects of shifts to atmospheric demand.
